---
title: "Lab 00 - Hello IDS!"
author: "Helen Miller"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Andrew", "Helen", "Adam", 
           "Max", "Sarah", "Liv"),
  github_username = c("pukklemaster", "helenrmiller", "adamlaycock", 
                      "MaxwellPohlman", "sarahstewart142", "oliviaharris1"), 
  colour = c("mediumaquamarine", "thistle1", "forestgreen", 
             "slategray3", "powderblue", "violetred"),
  hobby = c("knitting", "crochet", "guitar", 
            "climbing", "swimming", "netball"),
  favourite_number = c(7, 4, 7, 10, 6, 4)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


This visualization plots the data saved as teamdata as a bar chart and saves it as p1. On the x axis, usernames are shown. On the y axis, the corresponding numbers are shown. The bars are filled with each person's favourite colour.

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "Github Username", 
          y = "Favourite Number (1-10)",
          title = "General Information About IDS Group Members")
```

The labs() function adds labels to the plot.

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

This is a poor visualisation because there are too many possible observations for the categorical variable "hobby". This would be even worse if we included every member of the class, because very few people probably have the same hobbies. A better way to visualise this may be to assign each hobby obeservation to a general category (i.e. 'crafts', 'sports', 'music', etc.) and plot that variable instead.